---
title: "Depression Data Analysis"
author: "Becca DeCamp"
date: "10/7/2017"
output: html_document
---

I downloaded the data in an R data format directly off the online data repository I found it on. Here, I am loading that data in to R. As you see, I am pulling data from three different datasets in to this study, because the data was split up in to several different data frames (this is because it is a LOT of data). 

```{r}
get(load(file = "da36147.0003.rda"))

get(load(file = "da36147.0005.rda"))

get(load(file = "da36147.0008.rda"))

```

Now, I am concatenating the data in to one data frame (i.e. not only shoving all the data together, but aligning the data by the columns that the datasets have in common so the data for each person is aligned in one single row). I concatenated by household number, and by person number in that household. 
```{r}

newdata <- merge(da36147.0003, da36147.0005, by = c("HHX", "FPX"), all = TRUE)
head(newdata)

dep <- merge(newdata, da36147.0008, by = c("HHX", "FPX"), all = TRUE)
head(dep)
tail(dep)

```

As you can see, now we got all the data in to one place, but there's still way too much of it! Now I will filter the data and pull out only the columns we need from the 900-some columns that currently exist in the framework. 

```{r}
library(dplyr)

```

